---
title: "MMPD"
author: "Sayani Gupta"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "figure/",
  fig.align = "center",
  fig.show = "hold",
  cache = TRUE,
  cache.path = "cache/")

knitr::opts_knit$set(root.dir = here::here())
knitr::read_chunk('../_drake.R')
knitr::read_chunk('../packages.R')

#drake::loadd()

```

```{r load}
source("./packages.R")
source("./_drake.R")
library(tidyverse)
library(ggplot2)
library(distributional)
library(drake)
```

```{r level23}
nsim = 250
nperm = 1000
set.seed(99)
nx = 2
nfacet = 3
MMPD_data23 <- (1:nsim) %>% 
  purrr::map_df(function(i){
set.seed(99+i)
mmpd <- sim_panel(nx = 2, nfacet = 3) %>% 
  compute_quantiles() %>% 
  distance_panel() %>% 
  mpd() %>% 
  mmpd()

tibble(case = paste0("nx-",nx," ", "nfacet-", nfacet), sim_id = i, mmpd = mmpd)
  })
```

```{r plot23}
MMPD_data23 %>% ggplot(aes(x = mmpd)) + geom_histogram()
```


```{r level73}
nx = 7
nfacet = 3
set.seed(99)
MMPD_data73 <- (1:nsim) %>% 
  purrr::map_df(function(i){
set.seed(99+i)
mmpd <- sim_panel(nx = 7, nfacet = 3) %>% 
  compute_quantiles() %>% 
  distance_panel() %>% 
  mpd() %>% 
  mmpd()


tibble(case = paste0("nx-",nx," ", "nfacet-", nfacet), sim_id = i, mmpd = mmpd)
  })
```

```{r plot73}
MMPD_data73 %>% ggplot(aes(x = mmpd)) + geom_histogram()
```


```{r level37}
nx = 3
nfacet = 7
set.seed(99)
MMPD_data37 <- (1:nsim) %>% 
  purrr::map_df(function(i){
set.seed(99+i)
mmpd <- sim_panel(nx = 3, nfacet = 7) %>% 
  compute_quantiles() %>% 
  distance_panel() %>% 
  mpd() %>% 
  mmpd()


tibble(case = paste0("nx-",nx," ", "nfacet-", nfacet), sim_id = i, mmpd = mmpd)
  })
```

```{r plot37}
MMPD_data37 %>% ggplot(aes(x = mmpd)) + geom_histogram()
```


```{r level311}
nx = 3
nfacet = 11
set.seed(99)
MMPD_data311 <- (1:nsim) %>% 
  purrr::map_df(function(i){
    set.seed(99+i)
    mmpd <- sim_panel(nx = 3, nfacet = 11) %>% 
    compute_quantiles() %>% 
    distance_panel() %>% 
    mpd() %>% 
    mmpd()


    tibble(case = paste0("nx-",nx," ", "nfacet-", nfacet), sim_id = i, mmpd = mmpd)
  })
```

```{r plot311}
MMPD_data311 %>% ggplot(aes(x = mmpd)) + geom_histogram()
```


## Compare (1,1) vs (1,2) and (2,1) vs (2,2)

Difference between graphs in first row is the different in number of x levels. Difference between graphs in second row is the different in number of facet levels. For both the cases, the shape and scale of the distribution remains the same. 


## Compare (1,2) and (2,2)

But flipping the x-axis and facet levels change the distribution even when all levels are drawn from same distribution.This is logical since for normalising the x-axis, we use max and for facets we use median. AND we want to put more emphasis on differences in x-axis levels as than difference in facet-levels. Since, x-axis are from the same distribution and more in number, the final distribution is uniform-like.


```{r plotnew6}
library(forcats)
data_orig <- bind_rows(MMPD_data23, MMPD_data73, MMPD_data311, MMPD_data37) %>% 
  mutate(case = factor(case, 
                       levels = c("nx-2 nfacet-3",
                                  "nx-7 nfacet-3",
                                  "nx-3 nfacet-11",
                                  "nx-3 nfacet-7")))
  
data_orig %>% ggplot(aes(x = mmpd)) + facet_wrap(~case, ncol = 2) + geom_histogram()
          
          
          #MMPD_data37, MMPD_data73, MMPD_data311) %>% 
```

