---
title: "Characteristics of mmpd"
author: "Sayani Gupta"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "figure/",
  fig.align = "center",
  fig.show = "hold",
  cache = TRUE,
  cache.path = "cache/")

knitr::opts_knit$set(root.dir = here::here())
```

```{r load}
library(drake)
library(tidyverse)
library(knitr)
loadd()
```

## Primary objective: Studying null distribution of MMPD

  - How mmpd varies across x-axis levels for the same facet level?
  - How mmpd varies across facet levels for the same x-axis level?
  - Does normalisation work for both x-axis and facets?
  - If no, is it failing for x-axis, facet or both?

## Approach:

Panel grid of x-axis levels (nx) and facet levels (nfacet). If we see across rows, we will know the effect of changing facets for the same number of x-axis levels and across columns, we will know the effect of changing x-axis levels for the same facet. This would help us to judge if normalisation is not working at one or both levels.

## Step1 
_*simulate a grid of data for a combination of a range of x-axis and facet levels with same distribution*_

```{r sim_null_orig}
data <- readd(sim_null_orig)
data %>% 
  group_by(nx, nfacet) %>% 
  nest() 
```

## Step2 
_Compute a grid of mmpd for the simulated data in step 1_

```{r}
readd(mmpd_null_orig)

```

## Step3 
_Shuffle the data nsim times and compute grids of mmpd like in step 2 */nsim/* times_

```{r}
data <- readd(mmpd_dist_null_grid)
data %>% 
  group_by(nx, nfacet) %>% 
  nest() 
```

## Step4
_visualise the distribution of mmpd in each grid_ 


```{r}
readd(plot_dist_null_grid)
```

## Step5
_size of the test_ 

```{r}
readd(plot_dist_null_grid)
```

## Analysis

## Reproducibility

<details><summary>Reproducibility receipt</summary>

```{r}
## datetime
Sys.time()

## repository
if(requireNamespace('git2r', quietly = TRUE)) {
  git2r::repository()
} else {
  c(
    system2("git", args = c("log", "--name-status", "-1"), stdout = TRUE),
    system2("git", args = c("remote", "-v"), stdout = TRUE)
  )
}

## session info
sessionInfo()
```

</details>
